%
%
% Copyright (c) 2012 Benjamin Geiger <copyright@bgeiger.net>
\documentclass{article}
%\usepackage{indentfirst}
\usepackage{hyperref}

%\usepackage[pdftex]{graphicx}
%\DeclareGraphicsExtensions{.pdf,.jpg,.png}

\title{Project Proposal}
\author{Benjamin Geiger\\
Andrew Price}
\date{6 March 2013}

\begin{document}

\maketitle

\section{Introduction}

As social media sites become more popular, these websites have a vested
interest in determining which sections their users visit, as well as
target advertising. One such site is ``Reddit'', a user-driven
communication board and news aggregator. Reddit accepts news submissions
from users and collects them into separate communities, known as
``subreddits''. Users then decide which subreddits they wish to see when
reading the site.

For this project, we plan on mining data from a large social media site,
and attempting to both profile individual users and determine which
sections of the website they would be interested in. The commercial
applications of such a project should be obvious.

\section{Deliverables}

The planned deliverables at this point include a report on our findings,
as well as detailed data. This report will include discussions on our
findings, as well as a high-level outline of code.

\section{Methodology}

Reddit publishes a data access API for use by application developers. We
intend to use this API to acquire information about the site's users and
subreddits. We can then determine the users' interests, with which we
can then suggest subreddits they may be interested in, as well as
advertisers.

\section{Resources}

We initially intend to work with the Python language, using the PRAW
(Python Reddit API
Wrapper)\footnote{\url{https://praw.readthedocs.org/en/latest/}} or
ReddiWrap\footnote{\url{https://github.com/derv82/reddiwrap/}}
libraries.

\section{Schedule}

Our first milestone is to get a better understanding the required
libraries as well as clustering algorithms. The second milestone will be
to find all subreddits visited by any user of a given subreddit.
Currently, this is the extent of the analysis conducted on reddit users.
Finally, we plan on writing the prediction algorithm for the data we
collect.

\nocite{*}
\bibliographystyle{plain}
\bibliography{proposal}

\end{document}


